\documentclass[]{deedy-resume-openfont}
\usepackage{relsize}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\smaller
\namesection{Brahm Prakash}{Mishra}{
\href{mailto:bpmishra92@gmail.com}{\custombold{\underline{Email:}}bpmishra92@gmail.com} \hskip 7em \href{github.com/brainwave}{\custombold{\underline{Github:}}github.com/brainwave} \\
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{EDUCATION}
\subsection{National Institute of} \subsection{Technology, Trichy }

\descript{B.Tech in Mechanical Engineering}
\location{May 2010 - May 2014}
\location{Graduated in May 2014}
\location{ Cumulative GPA: 8.99 / 10.00 }
\sectionsep

\subsection{University of California} \subsection{San Diego} 
\descript{Graduate Studies}
\location{Sep 2016 - Sep 2017}
\location{ Credits Earned: 21 / 36 }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}

\subsection{Graduate}
Robot Motion Planning\\
Concurrent Embedded Systems\\
Analysis of Numerical Algorithms\\
Human-Computer Interface Design\\
Control System Design\\
Optimal Estimation\\
Robot Manipulation\\

\sectionsep{}

\subsection{Undergraduate}
Computer Aided Design \\
Applied Electronics and Electrical Engineering\\
Mechatronics \\
Computational Fluid Mechanics\\
Finite Element Analysis\\
Corporate Communications\\
Professional and Business Writing\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

\subsection{Programming Languages}

Go \textbullet{} C++ \textbullet{} Python \\C \textbullet{}
R \textbullet{} SQL \textbullet{} VB.Net \\
Sharepoint \textbullet{} Excel VBA\\
Shell Scripting(Bash)

\sectionsep

\subsection{Packages/Frameworks}

Tensorflow \textbullet{}Numpy, Scipy  \\ 
MS SQL \textbullet{} SSIS \textbullet{} SSAS \\
ROS \textbullet{}  OpenGL \textbullet{} OpenMP 
MATLAB, Simulink \textbullet{}
V-Rep \textbullet{} Vim \textbullet{} \LaTeX 

\sectionsep

\subsection{Spoken Languages}
English \textbullet{} Hindi \textbullet{} Oriya \\
Tamil

%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Experience}

\runsubsection{ Bolt 3D Printers Private Limited }\\
\descript{Design and Implementation Engineer }
\location{December 2015 - September 2016 | Chennai, India }
\vspace{\topsep}
\begin{tightemize}
\item  Led a 6 person team that designed and built an industrial grade slicer software for an SLA 3D Printer. A slicer converts 3D model of an object into stacks of 2D cross sections suitable for printing.
\item Optimized the slicer to bring down its execution time from 5 minutes to 0.35 seconds on a standard model.
\item Designed and Prototyped a novel, continuous SLA 3D Printer. Researched for patentability.
%\item Experience in software and hardware aspects of new design. 
%\item Hands on experience in Design for Conformance, Manufacturability, Serviceability and Reliability.
\end{tightemize}

\sectionsep{}

\runsubsection{ Thorogood Associates}\\
\descript{Business Intelligence and Analytics Consultant}
\location{ July 2014 - August 2015 | Bangalore, India }
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
	\item Supported and Enhanced of Production Systems for British Sugar, built using Microsoft BI Suite. 
	\item Responsible for prevention and resolution of critical system errors. 
	\item EPOS Data Analysis and Reporting for Japan Tobacco International.
	\item Development and Support projects for Thorogood Management Information and Planning System (MIPS).
\end{tightemize}
\sectionsep



\runsubsection{ Robotics and Machine Intelligence Group }\\
\descript{ Head, Programming and Embedded Systems  }
\location{ NIT Trichy, India}
\location{ September 2013 - May 2014 | Trichy, India }
\begin{tightemize}
\item Undertook individual and group projects in experimental robotics.
\item Hands-on experience with CAD, CAM and CAE process on novel contraptions.
\item Mentored sophomors and led teams that participated in national level Robotics competitions in engineering colleges across India.
\end{tightemize}
\sectionsep


\runsubsection{ Molecular Dynamics Lab, IIT Bombay}\\
\descript{ Junior Summer Research Fellow }
\location{ May 2013 - August 2013 | Mumbai, India}
\begin{tightemize}
	\item Built a Linux Beowulf cluster using 40 itanium processors
  	\item Implemented massively parallel monte carlo simulations
\end{tightemize}
\sectionsep


\runsubsection{ Central Tool room \& Training Centre}\\
\descript{ Engineering Intern }
\location{ May 2012 - July 2012 | Bhubaneshwar, India}
\begin{tightemize}\item CAD/CAM/CAE of Volkswagen V Engine Parts
\item Process Optimization of ISRO PSLV C-11 Rocket components
\end{tightemize}
\sectionsep

%\section{Other Experience}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand\Topstrut{\rule{0pt}{2.1ex}}
\newcommand\Bottomstrut{\rule[-0.6ex]{0pt}{0pt}}

\section{Representative Projects}
\begin{tabular}{rll}

YEAR	     & Prof./Team  & Project Title \\
\hline
% 2014\Topstrut	& Dr. K. Pannirselvam  & Rapid and Reconfigurable  Metal Forming\\
            % &                  & Machine\\ 
2017	     & Dr. Rajesh Gupta & Realtime Air Traffic Control System \\ 
2016         & Dr. Sonia Martinez & Parallelized Motion Planning in Randomized Environments\\
2016         &Dr. R. Bitmead & Control System Design for a mobile unstable wheeled robot\\
2014	     & RMI  & Designd and Fabricated a Low Cost 3-D Printer\\
% 2013	     & RMI & Rehabilitative Exoskeleton\\
2012	     & RMI & Design, Fabrication and Reliability Testing of a High Speed \\& & Autonomous All Terrain Vehicle\\
2012	     & RMI & Interfacing the Kinect  with TI Pandaboard using Robot \\& & Operating System (ROS)\\
2011         & RMI & Inverse Kinematics of  a 3-DOF Sketching Arm \\
2011        &  Individual Projects & Maze Solvers, Tracking Robots, etc.\\
%2010        &  Ubuntu   & Contributor to 100 papercuts Project
\end{tabular}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% \section{Awards} 
% \begin{tabular}{rlll}
% YEAR	     & Level  & Awarding Body & Description\\
% \hline

% 2014 & 1st, National & Pragyan Techfest & Android One Robotics Event \Topstrut\\
% 2013 & National & Indian Academy of Sciences & Summer Research Fellowship\\
% 2013 & 1st, College & Synergy, NITT & Automatic Trebuchet \\
% 2011 & 1st, College & NIT Trichy & Autonomous Line Follower  \\ 
%      &              &            & Competition\\
% 2009 & 1st, Clusters & JNSE & Automatic Cement Curing System\\
% 2008 & 1st, National & JNSE & Modified Wind Turbine Design

% \end{tabular}
% \sectionsep


\end{minipage} 
\end{document}  \documentclass[]{article}
