\documentclass[]{deedy-resume-openfont}
\usepackage{relsize}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\smaller
\namesection{Brahm Prakash}{Mishra}{
\href{mailto:bpmishra92@gmail.com}{\custombold{\underline{Email:}}bpmishra92@gmail.com} \hskip 7em \href{github.com/brainwave}{\custombold{\underline{Github:}}github.com/brainwave} \\
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{EDUCATION}

\sectionsep
\subsection{National Institute of} \subsection{Technology, Trichy }

\descript{B.Tech in Mechanical Engineering}
\location{May 2010 - May 2014}
\location{ Cumulative GPA: 8.99 / 10.00 }
\sectionsep

\subsection{University of California} \subsection{San Diego} 
\descript{Graduate Studies}
\location{Sep 2016 - Sep 2017}
\location{ Credits Earned: 21 / 36 }

\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

\sectionsep

\subsection{Programming}

C++ \textbullet{} Embedded C \textbullet{} Go\\
Python \textbullet{} Shell Scripting(Bash)

\sectionsep

\subsection{Frameworks}

Tensorflow (learning) \textbullet{} ROS \\
Gazebo \textbullet{}  OpenGL \textbullet{} OpenMP \\
MATLAB, Simulink \textbullet{}  GNU/Linux \\
CATIA \textbullet{} Microsoft BI Suite \\
(SQL, SSIS, SSAS, SSRS)\\

\sectionsep

\subsection{Languages}
English \textbullet{} Hindi \textbullet{} Oriya \\
Tamil (Spoken)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\sectionsep
\section{Coursework}

\sectionsep

\subsection{Graduate}
Robot Motion Planning\\
Control System Design\\
Optimal Estimation\\
Analysis of Numerical Algorithms\\
Human-Computer Interface Design \\ Research\\
Embedded Software Systems\\
(Distributed and Concurrent)

\sectionsep{}

\subsection{Undergraduate}
Applied Electronics and Electrical Engineering\\
Mechatronics \\
Computer Graphics Software Design \\
Computational Fluid Mechanics\\
Finite Element Analysis\\
Corporate Communications\\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Experience}

\sectionsep

\runsubsection{ Bolt 3D Printers Private Limited }\\
\descript{Design and Implementation Engineer }
\location{December 2015 - September 2016 | Chennai, India }
\vspace{13pt}
\begin{tightemize}
\item  Led a 6 person team that built an industrial grade slicer software for an SLA 3D Printer. A slicer converts 3D model of an object into stacks of 2D cross sections suitable for printing. \hfill {\fontspec[Path = fonts/lato/]{Lato-LigIta}
\selectfont 
C++
} 
\item Used OpenGL and Algorithm optimizations to reduce slicer execution time from 5 min to 0.35 seconds on a standard model. \hfill {\fontspec[Path = fonts/lato/]{Lato-LigIta}
\selectfont 
OpenGL, Boost
}
\item Firmware and controller design for continuous SLA 3D Printer.\hfill {\fontspec[Path = fonts/lato/]{Lato-LigIta}
\selectfont 
AVR C, Python
}
\item Researched for patentability - helped frame provisional specification.
%\item Experience in software and hardware aspects of new design. 
%\item Hands on experience in Design for Conformance, Manufacturability, Serviceability and Reliability.
\end{tightemize}

\sectionsep{}

\runsubsection{ Thorogood Associates}\\
\descript{Business Intelligence and Analytics Consultant}
\location{ July 2014 - August 2015 | Bangalore, India }
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Support and enhancement production systems for Silver Spoon, a British Sugar subsidiary \hfill {\fontspec[Path = fonts/lato/]{Lato-LigIta}
\selectfont MS BI Suite}
	\item Responsible for prevention and resolution of critical system errors.  
	\item EPOS Data Analysis and Reporting for Japan Tobacco International. \hfill{\fontspec[Path = fonts/lato/]{Lato-LigIta}
\selectfont SQL, .Net}
	\item Development and Support projects for Thorogood Management and Information Planning System - MIPS. \hfill{\fontspec[Path = fonts/lato/]{Lato-LigIta} \selectfont C\#}
\end{tightemize}
\sectionsep

\runsubsection{ Robotics and Machine Intelligence Group (RMI)}\\
\descript{Programming Team Lead}
\location{ NIT Trichy, India}
\location{ September 2013 - May 2014 | Trichy, India }
\vspace{\topsep}
\begin{tightemize}
\item Undertook individual and group projects in experimental robotics \hfill{\fontspec[Path = fonts/lato/]{Lato-LigIta} \selectfont (below)}
\item Hands-on experience with CAD/CAM/CAE processes on novel contraptions.
\end{tightemize}
\sectionsep

\runsubsection{ Molecular Dynamics Lab, IIT Bombay}\\
\descript{ Junior Summer Research Fellow }
\location{ May 2013 - August 2013 | Mumbai, India}
\vspace{\topsep}
\begin{tightemize}
\item Built a Linux Beowulf cluster using 40 itanium processors. \hfill{\fontspec[Path = fonts/lato/]{Lato-LigIta} \selectfont CentOS}
\item Implemented massively parallel monte carlo simulations. \hfill{\fontspec[Path = fonts/lato/]{Lato-LigIta} \selectfont OpenMP, C++}
\end{tightemize}
\sectionsep


\runsubsection{ Central Tool room \& Training Centre}\\
\descript{ Engineering Intern }
\location{ May 2012 - July 2012 | Bhubaneshwar, India}
\vspace{\topsep}
\begin{tightemize}\item CAD/CAM/CAE of Volkswagen V Engine Parts. \hfill{\fontspec[Path = fonts/lato/]{Lato-LigIta} \selectfont CATIA}
\item Process Optimization of ISRO PSLV C-11 Rocket components. \hfill{\fontspec[Path = fonts/lato/]{Lato-LigIta} \selectfont Stochastic QC}
\end{tightemize}
\sectionsep

%\section{Other Experience}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand\Topstrut{\rule{0pt}{2.1ex}}
\newcommand\Bottomstrut{\rule[-0.6ex]{0pt}{0pt}}

\section{Representative Projects}
\begin{tabular}{rll}

YEAR	     & Prof./Team  & Project Title \\
\hline
            % &                  & Machine\\ 
2017\rule{0pt}{3ex}	     & Dr. Rajesh Gupta & Realtime air traffic control system in Golang\\ 
2016         & Dr. Sonia Martinez & Parallelized Motion Planning in randomized environments\\
2016         &Dr. R. Bitmead & Control system design for a mobile unstable wheeled robot\\
2014	     & Dr. K. Pannirselvam  & Rapid Desktop Metal Forming\\
2014	     & RMI  & Low cost 3-D printer using automobile parts\\
2013	     & RMI & Chasis design for a high speed ATV\\
2012	     & RMI & Kinect-Pandaboard interface Through ROS\\
2011        &  Individual Projects & Maze Solvers, tracking Robots, etc.\\
%2010        &  Ubuntu   & Contributor to 100 papercuts Project
\end{tabular}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% \section{Awards} 
% \begin{tabular}{rlll}
% YEAR	     & Level  & Awarding Body & Description\\
% \hline

% 2014 & 1st, National & Pragyan Techfest & Android One Robotics Event \Topstrut\\
% 2013 & National & Indian Academy of Sciences & Summer Research Fellowship\\
% 2013 & 1st, College & Synergy, NITT & Automatic Trebuchet \\
% 2011 & 1st, College & NIT Trichy & Autonomous Line Follower  \\ 
%      &              &            & Competition\\
% 2009 & 1st, Clusters & JNSE & Automatic Cement Curing System\\
% 2008 & 1st, National & JNSE & Modified Wind Turbine Design

% \end{tabular}
% \sectionsep


\end{minipage} 
\end{document}  \documentclass[]{article}
